Manuscript Figures for Genome Biology

### 2018-06-22 manuscript_figures/manuscript_figures.Rmd
Add Supp figure to compare ranks in sim vs casestudies

xtable(tabS3)
```

@@

ggdraw() +
  draw_plot(pfdr + ylab("") + xlab(""), 0.57, 0, 0.22, 1) +
  draw_plot(ptpr + ylab("") + xlab(""), 0.78, 0, 0.22, 1) +
  draw_plot(Fig4, 0, 0, 0.60, 1) +
  draw_plot_label(c("A", "B"), c(0, 0.57), c(1, 1), size = 15)
ggsave(file.path(outdir, "Figure4.pdf"), width=12, height=5)
```

>>>>

xtable(tabS3)

# generate detailed case study table for creating sim vs cs ranks boxplots
casestudy.tab <- plotMethodRanks(objects, colLabels = dataset, alpha = alpha,
                                 tableOnly = TRUE)
```

@@

ggdraw() +
  draw_plot(pfdr + ylab("") + xlab(""), 0.57, 0, 0.22, 1) +
  draw_plot(ptpr + ylab("") + xlab(""), 0.78, 0, 0.22, 1) +
  draw_plot(Fig4, 0, 0, 0.60, 1) +
  draw_plot_label(c("A", "B"), c(0, 0.57), c(1, 1), size = 15)
ggsave(file.path(outdir, "Figure4.pdf"), width=12, height=5)

# generate detailed case study table for creating sim vs cs ranks boxplots
yeastsim.tab <- plotMethodRanks(objs, colLabels = labs, alpha = alpha,
                                 tableOnly = TRUE)
```

Create boxplot of ranking in sims versus rankings in case studies using the
`casestudy.tab` and `yeastsim.tab` objects created above.

```{r}
casestudy.tab <- mutate(casestudy.tab, prop_casestudy = mean_prop) %>%
  select(casestudy, method, prop_casestudy)
yeastsim.tab <- yeastsim.tab %>% 
  mutate(prop_yeastsim = mean_prop) %>% 
  filter(casestudy == "de5") %>%
  select(casestudy, method, prop_yeastsim)

rank.tab <- left_join(casestudy.tab, yeastsim.tab, by = "method") %>%
  left_join(candycols %>% dplyr::mutate(method=Method), by = "method")

col <- as.character(rank.tab$col)
names(col) <- as.character(rank.tab$method)

rank.tab$method <- factor(rank.tab$method,
                          levels = yeastsim.tab$method[order(yeastsim.tab$prop_yeastsim)])

ggplot(rank.tab, aes(y = prop_casestudy, x = method, group = method, fill = method)) +
  geom_boxplot() +
  scale_fill_manual(values=col) +
  theme_bw() +
  xlab("Method (ordered by rejections in Yeast simulation (n=5))") + 
  ylab("Proportion of maximum rejections in casestudies")
ggsave(file.path(outdir, "Figure_simVcasestudyRanks.pdf"), width=6, height=4)
```
